Luminosity function and flux function\\ or\\ How far to the brightest beacon?

### 2015-12-15 luminosity.tex
explanation about the fact that n_r is an expected value

Let us consider the distribution of fluxes from sources from a spherical shell at distance $r$ with thickness $dr$.
The ({\it expected}) total number of the sources within that spherical shell is
%%%
\begin{equation}
n_r \equiv dr \int _0 ^{\infty} \frac{d^2 N}{dF~dr} dF \, . 
\end{equation}
%%%
\memoYF{not sure how to deal with the fact that this is expected number.}

The probability that a source within the spherical shell has a flux between $F\sim F+dF$, $P[F]dF $, may be assumed to be proportional to the flux number distribution given by equation (\ref{eq:dNdFdr}):
%%%
\begin{equation}
P[F] dF = \left\{
\begin{array}{ll}
C' F^{\alpha } r^{4-2\alpha } dF & (F_{\rm min}(r) < F < F_{\rm max}(r)) \\
0 & (\mbox{elsewhere})
\end{array}
\right. 
\end{equation}
%%%
where
%%%
\begin{eqnarray}
C' &=& n_r \left( \int _0 ^{\infty}P[F]~dF~\right)^{-1} \\
F_{\rm min}(r) &=& L_{\rm max} / 4 \pi r^2 \\
F_{\rm max}(r) &=& L_{\rm max} / 4 \pi r^2
\end{eqnarray}
%%%

The probability that the bright flux lies in the range between $F_{\rm bright}$ and $F_{\rm bright} + dF_{\rm bright}$, denoted $\mathcal{P} [F_{\rm bright}] dF_{\rm bright}$, is the joint probability that one of the targets has flux between $F_{\rm bright}$ and $F_{\rm bright} + dF_{\rm bright}$ and that all others have smaller flux.
The probability that one object has flux lower than $F'$ is
%%%
\begin{equation}
P [<F'] = \int _{-\infty} ^{F'}  P [F] \; dF 
\end{equation}
%%%
Noting that we have $n_r$ ways to select the target with the highest flux, this probability is:
%%%
\begin{equation}
\mathcal{P} [F_{\rm bright}] dF_{\rm bright} = n_r P [< F_{\rm bright}]^{n_r-1}  P[F_{\rm bright}] dF_{\rm bright} %\\
%&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
%&\sim & N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - ( N_R -1 ) P (> F_{\rm max}) \right]
\end{equation}
%%%

>>>>

Let us consider the distribution of fluxes from sources from a spherical shell at distance $r$ with thickness $dr$.
The ({\it expected}) total number of the sources within that spherical shell is
%%%
\begin{equation}
n_r \equiv dr \int _0 ^{\infty} \frac{d^2 N}{dF~dr} dF \label{eq:n_r}\, . 
\end{equation}
%%%
Note that the result of the right hand side is actually the {\it expected} number and, in reality, the source count should be an integer with some occurrence probability around this expected number.

The probability that a source within the spherical shell has a flux between $F\sim F+dF$, $P[F]dF $, may be assumed to be proportional to the flux number distribution given by equation (\ref{eq:dNdFdr}):
%%%
\begin{equation}
P[F] dF = \left\{
\begin{array}{ll}
C' F^{\alpha } r^{4-2\alpha } dF & (F_{\rm min}(r) < F < F_{\rm max}(r)) \\
0 & (\mbox{elsewhere})
\end{array}
\right. 
\end{equation}
%%%
where
%%%
\begin{eqnarray}
C' &=& \left( \int _{F_{\rm max}} ^{F_{\rm min}} F^{\alpha } r^{4-2\alpha } dF~dF~\right)^{-1} \\
F_{\rm min}(r) &=& L_{\rm max} / 4 \pi r^2 \\
F_{\rm max}(r) &=& L_{\rm max} / 4 \pi r^2
\end{eqnarray}
%%%

The probability that the bright flux lies in the range between $F_{\rm bright}$ and $F_{\rm bright} + dF_{\rm bright}$, denoted $\mathcal{P} [F_{\rm bright}] dF_{\rm bright}$, is the joint probability that one of the targets has flux between $F_{\rm bright}$ and $F_{\rm bright} + dF_{\rm bright}$ and that all others have smaller flux.
The probability that one object has flux lower than $F'$ is
%%%
\begin{equation}
P [<F'] = \int _{-\infty} ^{F'}  P [F] \; dF 
\end{equation}
%%%
Noting that we have $n_r$ ways to select the target with the highest flux, this probability is:
%%%
\begin{equation}
\mathcal{P} [F_{\rm bright}] dF_{\rm bright} = n_r P [< F_{\rm bright}]^{n_r-1}  P[F_{\rm bright}] dF_{\rm bright} %\\
%&=& N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - P (> F_{\rm max}) \right]^{N_R-1} \\
%&\sim & N_R P(F_{\rm max}) dF_{\rm max} \left[ 1 - ( N_R -1 ) P (> F_{\rm max}) \right]
\end{equation}
%%%
Here, the right thing to do would be to take an infinite sum over integer values of $n_r$ with occurrence probability function, but for the sake of simplicity, here we simply assume $n_r$ computed by equation (\ref{eq:n_r}) is a good proxy.
